Multimodal Corpora

### 2017-01-15 paper.tex
Write first two subsections for the second corpus

%
\begin{document}

@@

	\section{Second Corpus}
		\Todo{Add second corpus}

>>>>

\newacronym{callas}{Callas}{Conveying Affectiveness in Leading edge Living Adaptive Systems}
%
\begin{document}

@@

	\section{The CALLAS Expressivity Corpus}
		The yet to be released CALLAS Expressivity Corpus is part of the \gls{callas} project \cite{2010MultimodalCorpusForGestureExpressivity}. It was introduced in 2010 \cite{2010MultimodalCorpusForGestureExpressivity} and further described in \cite{Caridakis2013} three years later. All the information in this section is taken from those two papers if not stated otherwise, as this corpus was not released to the public yet, so there is no other information source besides a paper from one of the collaborators\cite{wagner:2011:1}. This corpus was a collaboratiove work between the National Technical University of Athens (G. Caridakis, A. Raouzaiou, K. Karpouzis), the Augsburg University (J. Wagner, F. Lingenfelser, E. Andre) and Humanware S.r.l. (Z. Curto). The available modalities are audio, video and hand gestures recorded separately in three different ways. 
		\subsection{Motivation}
			The main focus for this corpus was to capture cross-cultural differences in expressing emotoions with hand gestures. Obtaining the data which is needed to investigate the differences in cultures was done by collecting data in Greece, Germany and Italy as well. Another motivation was the recording of material which is as realistic as possible. This led the team to use persons without any background as actor, with the result that the data's variance is high, which is better to model the real world as the emotion expression of humans may vary greatly.
